Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-01-18 paper/main.tex
Replace eq_comparison_PNAS with individual subfigures generated by forcesim_rsi21.m

\begin{figure}[ht]
\centering
\includegraphics[width=.48\textwidth]{figures/eq_comparison_PNAS}
\caption{Comparison between terms of the analytical expressions (red) and data-driven models (blue).
  (A) Primary translational aerodynamic lift proportional to the square of the wing velocity. (B)
  Inertial forces related to the pendulum motion of the wing and deviation out of the stroke plane.
  The modeling process automatically decoupled aerodynamic and inertial effects with no prior
  knowledge of the system.  The total measured force is shown for reference (black).}
\label{fig:eqcomparison}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/eq_comparison_lift}
\caption{\label{fig:eqcomparison_lift}}
\end{subfigure}
% \qquad
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/eq_comparison_inertial}
\caption{\label{fig:eqcomparison_inertial}}
\end{subfigure}
\caption{Comparison between terms of the analytical expressions (red) and data-driven models (blue).
  \subref{fig:eqcomparison_lift} Primary translational aerodynamic lift proportional to the square
  of the wing velocity. \subref{fig:eqcomparison_inertial} Inertial forces related to the pendulum
  motion of the wing and deviation out of the stroke plane. The modeling process automatically
  decoupled aerodynamic and inertial effects with no prior knowledge of the system. The total
  measured force is shown for reference (black).}
\label{fig:eqcomparison}
\end{figure}
